---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Alex Ivanova"
date: "7/30/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Presentation

The goal of the project is to create a Shiny application and deploy it on Rstudio's servers, and then use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application.

## Data Used

The data used for the regression analysis is a classic mtcars data that was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r looking at data}
str(mtcars)
```

## The Main Idea

The app asks you to select the amount of horsepower, according to which it will predict the car's mpg using the regression model.
The app can be found here: https://alexivanova.shinyapps.io/shinyapp/
ui.R, and Server.R Code are in my github repository: https://github.com/AlexIvanova/DDP_courseProj

## Plot

The plot for hp ~ mpg looks like this.
```{r plot}
plot(hp ~ mpg, mtcars)
```